### 2020-04-29 README.Rmd
Changed the idea of a plots to a results subdirectory within the rundir. Also simplified the plotting of the production graphs by altering plotprod. No errors, no warnings, no notes.

* population - literally a population. These are the active components within the simulation framework. The dynamics of the simulation are based around the populations, although, with positive larval dispersal (the default) there is some dependency of neighboiuring populations on each other.

This conceptual structure has implications for how the simulations are conditioned during the management strategy testing. While it is still the case tha tthe general properties of each SMU are used to set the scene for each SMU's component populations, the advent of sufficient GPS logger data now allows a more formal definition of the productivity of each population. Currently, the modelling assumes that each population is linearly arranged around the coastline, and this will allow, where available, specific catch/yield data to be used to define the bounds of each population within an SMU.

@@

>>>>

* population - literally a population. These are the active components within the simulation framework. The dynamics of the simulation are based around the populations, although, with positive larval dispersal (the default) there is some dependency of neighbouring populations on each other.

This conceptual structure has implications for how the simulations are conditioned during the management strategy testing. While it is still the case that the general properties of each SMU are used to set the scene for each SMU's component populations, the advent of sufficient GPS logger data now allows a more formal definition of the productivity of each population. Currently, the modelling assumes that each population is linearly arranged around the coastline, and this will allow, where available, specific catch/yield data to be used to define the bounds of each population within an SMU.

@@

### 29/04/2020

Now developing a vignette entitled _Running_aMSE_, which contains some worked examples to get a user moving in the uise of __aMSE__. There remains much development still to do.
